---
title: "Sales and Revenue of ExxonMovil"
author: "Miguel Angel Bustos"
date: "04-01-2022"
output:
  pdf_document: default
  html_document: default
---

**Sales and Revenue Differences**

What´s the difference between Sales and Revenue? ExxonMovil, it´s an american multinational oil and gas corporation, headquartered in Irving, Texas. And this is the "ExxonMovil Condensed Consolidated Statement of Income" in 2019:

 \fbox{CCSOI = Condensed Consolidated Statement of Income}

 \fbox{Sales = Money paid by customers}

 \fbox{Revenue = (i) Sales, (ii) Income form equity affiliates and (iii) other incomes}



```{r, include=F}

library(ggplot2)
library(tidyverse)

```

1.- This is the ExxonMovil Condensed Consolidated Statement of Income data frame:

```{r}

CCSOI <- data.frame(Revenues_and_other_Income = c("Sales and operating revenue",
                                                  "Income form Equity Affiliaties",
                                                  "Other Income"),
                    Thirteenth_June_2019 = c(67491, 1359, 241),
                    Thirteenth_June_2018 = c(71456, 1729, 316))

```



2.- Set up this code to construct a geom bar:


```{r}

r <- ggplot(data = CCSOI, aes(x = "", y = Thirteenth_June_2019, fill = Revenues_and_other_Income))
r+ geom_bar(stat = "identity") +
  ylab("2019 incomes")+
  xlab("Revenue") +
  ggtitle("Revenue composition", subtitle = "The revenue concept") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_color_discrete(name = "Revenue of ExxonMovil")
  


```

3.- Conclusion: 

The Revenue is majority sales as this geom bar shows, but it´s important to consider "The incomes from equities" and "Other incomes".

[SOURCE: [ExxonMovil Condensed Consolidated Statement of Income]](https://www.investopedia.com/ask/answers/122214/what-difference-between-revenue-and-sales.asp)



